Efficient Coalition Formation for Web Services

### 2013-04-22 papers/coalition/SCC2013_WSCoalition.tex
Changes

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is tied to the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of any web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the least-core value using our
valuation function and our set of web services. We picked random
number of web services from the dataset and formed around 10,000
random coalitions consisting of 3 to 26 web services. We choose 26
as the maximum number of members in our grand coalition since it
is computationally very complex for bigger coalitions to compute
\emph{$\epsilon$-core}. We set $\epsilon$ to a ratio of total
payoff of coalition $v(C)$ between 0 and 1. The results in Figure
\ref{f_leastcore} illustrates that almost 10\% of our random web
service coalitions have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain 30\% more of $v(C)$ by deviating.

@@

As future work, we would like to perform more analytical and
theoretical analysis on the convexity condition for the
characteristic function on web service applications. From web service perspective, the
work can be extended to consider web service compositions where a
group of web services having different set of skills cooperate to
perform composite tasks. Also bargaining theory from cooperating
game theory concepts can be used to help web services resolve the
instability and unfairness issues by side payments.

>>>>

In this scenario, as new web services are discovered and get ready
to join communities, our algorithm keeps merging and splitting
partitions based on the preference function. The decision to merge
or split is based on the fact that all players must benefit. The
new web services will merge with communities if $all$ the players
are able to improve their individual payoff, and some web services
may split from old communities, if splitting does not decrease the
payoff of any web service of the community. According to
\cite{DBLP:journals/corr/abs-cs-0605132}, this sequence of merging
and splitting will converge to a final partition, where web
services cannot improve their payoff. More details of this
algorithm and analysis of generic solutions on coalition formation
games are described in \cite{DBLP:journals/igtr/AptW09}.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
valuation function and a set of web services. We picked random
number of web services from the dataset and formed around 10,000
random coalitions consisting of 3 to 26 web services. We choose 26
as the maximum number of members in our coalition since it
is computationally very complex for larger coalitions to verify whether 
\emph{$\epsilon$-core} set is empty or not. Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$.v(C)} by deviating. We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non emptiness. The results in Figure
\ref{f_leastcore} illustrates that almost 10\% of our random web
service coalitions have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain only 30\% more of $v(C)$ by deviating.

@@

As future work, we would like to perform more analytical and
theoretical analysis on the convexity condition and also minimal $\epsilon$ values in \emph{$\epsilon$-core} solution concepts based on the
characteristic function in web service applications. From web service perspective, the
work can be extended to consider web service compositions where a
group of web services having different set of skills cooperate to
perform composite tasks. Also bargaining theory from cooperating
game theory concepts can be used to help web services resolve the
instability and unfairness issues by side payments.
